Object Naming in Language and Vision: A Survey and a New Dataset

### 2019-11-29 papers/LREC2020/background.tex

The act of naming an object amounts to that of picking out a nominal to be employed to refer to it (e.g., ``the \refexp{dog}'', ``the white \refexp{dog} to the left'').
Since an object is simultaneously a member of multiple categories (e.g., a young beagle belongs to the categories \cat{dog}, \cat{beagle}, \cat{animal}, \cat{puppy}, \cat{pet}, etc.), all the various names that lexicalize these constitute a valid alternative, meaning that the same object can be named with different names \cite{brown1958shall,murphy2004big}.

Seminal work on concepts by \newcite{rosch1976basic} inspired a taxonomic view of object naming, in which names exhibit a preferred level of specificity called the ``entry-level'' \cite{jolicoeur1984pictures}. This typically corresponds to an intermediate level of specificity, i.e., basic level (e.g., \refexp{bird}, \refexp{car}), as opposed to more generic (e.g., \refexp{animal}, \refexp{vehicle}) or specific categories (e.g., \refexp{sparrow}, \refexp{convertible}). 
However, less prototypical members of basic-level categories tend to be instead identified with sub-level categories (e.g., a penguin is typically called \refexp{penguin} and not \refexp{bird}) \cite{jolicoeur1984pictures}. 
%This out-of-context preference towards a certain taxonomic level is often referred to as \textbf{lexical availability}. 
While the traditional notion of entry-level categories suggests that objects tend to be named by a \refexp{single} preferred concept, research on pragmatics has found that speakers are flexible in their choice of the level of specificity \cite{olson1970language,rohde2012communicating,graf2016animal}.
%Scenarios where multiple objects (of the same category) are present induce a pressure for generating names which uniquely identify the target \cite{olson1970language}, such that sub-level names can be systematically elicited in these cases \cite{rohde2012communicating,graf2016animal}.
For example, in presence of more than one dog, the name \textsl{dog} is ambiguous and a sub-level category (e.g., \textsl{rottweiler}, \textsl{beagle}) is potentially preferred by speakers.
%, though additional factors such as cost or saliency also come into play \cite{graf2016animal,clark1983common}.
The purely taxonomic view has been criticized in more recent work on concept organization, which found that many objects of our daily lifes are part of multiple category systems at the same time \cite{ross1999food,SHAFTO20111}. 
This \textit{cross-classification} occurs, for instance, with food categories which can be taxonomy-based (e.g.\ \refexp{meat, vegetable}) or script-based (e.g.\  \refexp{breakfast, snack}).
We provide tentative evidence that cross-classification is indeed relevant for naming variation, and that the taxonomic axis is not the main parameter that accounts for variation in our data.

@@

An important experimental paradigm in work on human vision and categorization is picture naming, where subjects have to say or write down the first name that comes to mind when looking at a picture of (typically) a line drawing depicting a prototypical instance of a category \cite{snodgrass,rossion2004revisiting}, see Figure\ \ref{fig:cake}.
Subjects reach very high agreement in this task \cite{rossion2004revisiting}, and the resulting naming norms are useful for studying various cognitive processes \cite{humphreys1988cascade}.
Our task is inspired by picture naming, but uses real-world images with objects highlighted in them.

@@

In Computer Vision, object recognition is typically modelled as a classification task where objects need to be categorized according to a given labeling scheme that can comprise thousands of different categories in state-of-the-art systems \cite{googlenet,ILSVRC15}. 
Current recognition benchmarks use labels and images from the ImageNet \cite{imagenet_cvpr09} taxonomy, and typically assume a single ground-truth label. 
The construction of ImageNet was set up as a two-stage procedure: (i) images for given nodes in the ontology where automatically collected by querying search engines, (ii) crowd-workers then verified whether each candidate image is an instance of the given category.
Other data collection efforts for object labels also used a predefined vocabulary and asked annotators to mark all instances of these categories in a set of images \cite{mscoco,OpenImages}. 
Recently, \newcite{pont2019natural} have argued for annotation of object labels using free form text though here this free vocabulary is then mapped to a set of underlying classes.
Thus, even though object recognition benchmarks do provide images of objects and categories, they generally do not provide what we are interested in in this work, namely natural names of objects.

@@

In contrast to work on object recognition, work in L\&V typically collects and uses data sets where annotators produce free and natural utterances for a given image. 
Moreover, these data sets typically record utterances that are more complex than a single word, such as image captions \cite{fangetal:2015,devlin:imcaqui,Bernardietal:automatic}, referring expressions \cite{Kazemzadeh2014,mao15,Yu2016}, visual dialogues \cite{das2017visual,vries2017guesswhat} or image paragraphs \cite{krause2017hierarchical}. While object names occur in all of these data sets, they are not necessarily marked up and linked to the corresponding image regions. The overview in the following Section \ref{sec:survey} will focus on corpora where the grounding of names to regions for objects is given, as in the case of \vgenome \cite{krishna2016visualgenome}, or where it can be easily derived, as in the case of referring expressions.

Our new collection, ManyNames, presented in Section \ref{sec:data} focusses on object names in in isolation and is, therefore, substantially more controlled than typical data sets that are currently in use in in L\&V. This controlled collection procedure, however, allowed us to elicit many annotations for the same object from different annotators, resulting in a data set that is amenable to studying variation and preferences in naming systematically and on a large scale.

\begin{table*}[htb]
  \centering
  \begin{tabular}{lrrrrr}
    \toprule
    &   RefCoco/+  &  Flickr30kE &           VG &      VGmn &        MN \\
    \midrule
    \# objects & 50.000 & 243.801 & 3.781.232 & 25.315 & 25.315 \\
    naming vocab size &  5.004 &  10.423 &   105.441 &  1.061 &  7.970 \\
    av. annotations/object &      2.8 &       2.3 &         1.7 &      7.2 &     35.3 \\
    \% objects with n types $>$ 1 &      0.7 &       0.3 &         0.02 &      0.05 &      0.9 \\
    av. types/object &      1.9 &       1.4 &         1 &      1.1 &      5.7 \\
    \bottomrule
  \end{tabular}
  \label{tab:compare}
  \caption{Overview statistics for different data sets containing object naming data. VGmn shows statistics for the subset of \vg that overlaps with our ManyNames dataset.}
\end{table*}

>>>>

The act of naming an object amounts to that of picking out a nominal to be employed to refer to it (e.g., ``the \refexp{dog}'', ``the white \refexp{dog} to the left'').
Since an object is simultaneously a member of multiple categories (e.g., a young beagle belongs to the categories \cat{dog}, \cat{beagle}, \cat{animal}, \cat{puppy}, \cat{pet}, etc.), all the various names that lexicalize these constitute a valid alternative, meaning that the same object can be called by different names \cite{brown1958shall,murphy2004big}.

Seminal work on objects\cs{only use object, not concept, otherwise we would unnecessarily need to explain it} by \newcite{rosch1976basic} inspired a taxonomic view of object naming, in which names exhibit a preferred level of specificity called the ``entry-level'' \cite{jolicoeur1984pictures}. 
This typically corresponds to an intermediate level of specificity (basic level,\ e.g., \refexp{bird}, \refexp{car}), as opposed to more generic (super-ordinate,\ e.g., \refexp{animal}, \refexp{vehicle}) or more specific categories (sub-ordinate,\ e.g., \refexp{sparrow}, \refexp{convertible}). \cs{Rosch uses the term 'level of abstraction'}
However, less prototypical members of basic level categories tend to be instead identified with sub-ordinate categories (e.g., a penguin is typically called \refexp{penguin} and not \refexp{bird}; \newcite{jolicoeur1984pictures}). 
%This out-of-context preference towards a certain taxonomic level is often referred to as \textbf{lexical availability}. 
While the traditional notion of entry-level categories suggests that objects tend to be named by a \refexp{single} preferred concept, research on pragmatics has found that speakers are flexible in their choice of the level of specificity \cite{olson1970language,rohde2012communicating,graf2016animal}.
%Scenarios where multiple objects (of the same category) are present induce a pressure for generating names which uniquely identify the target \cite{olson1970language}, such that sub-level names can be systematically elicited in these cases \cite{rohde2012communicating,graf2016animal}.
For example, in presence of more than one dog, the name \textsl{dog} is ambiguous and a sub-ordinate category (e.g., \textsl{rottweiler}, \textsl{beagle}) is potentially preferred by speakers.
%, though additional factors such as cost or saliency also come into play \cite{graf2016animal,clark1983common}.
The purely taxonomic view has been criticized in more recent work on object organization, which found that many objects of our daily lifes are part of multiple category systems at the same time \cite{ross1999food,SHAFTO20111}. 
This \textit{cross-classification} occurs, for instance, with food categories which can be taxonomy-based (e.g.\ \refexp{meat, vegetable}) or script-based (e.g.\  \refexp{breakfast, snack}).
We provide tentative evidence that cross-classification is indeed relevant for naming variation, and that the taxonomic axis is not the main parameter that accounts for variation in our data.

@@

An important experimental paradigm in work on human vision and categorization is picture naming, where subjects have to say or write down the first name that comes to mind when looking at a picture of (typically) a line drawing depicting a prototypical instance of a category \cite{snodgrass,rossion2004revisiting}, see Figure\ \ref{fig:cake}.
Subjects reach very high agreement\cs{what does agreement mean? \ra e.g., their is a clear tendency towards a certain name across all speakers?} in this task \cite{rossion2004revisiting}, and the resulting naming norms are useful for studying various cognitive processes \cite{humphreys1988cascade}.
Our task is inspired by picture naming, but uses real-world images with objects highlighted in them.

@@

In Computer Vision, object recognition is typically modeled as a classification task where objects need to be localized and categorized according to a given labeling scheme, which can comprise thousands of different categories, in \cs{? by?with?} state-of-the-art systems \cite{googlenet,ILSVRC15}. 
Current recognition benchmarks use labels and images from the ImageNet \cite{imagenet_cvpr09} ontology, and typically assume a single ground-truth label. 
The construction of ImageNet was set up as a two-stage procedure: (i) images for given categories in the ontology where automatically collected by querying search engines, (ii) crowd-workers then verified whether each candidate image is an instance of the given category.
Other data collection efforts for object labels also used a predefined vocabulary and asked annotators to mark all instances of these categories in a set of images \cite{mscoco,OpenImages}. 
Recently, \newcite{pont2019natural} have argued for annotation of object labels using free form text though here this free vocabulary is then mapped to a set of underlying classes.
Thus, even though object recognition benchmarks do provide images of objects and categories, they generally do not provide what we are interested in in this work, namely natural names of objects.

@@

In contrast to work on object recognition, work in L\&V typically collects and uses data sets where annotators produce free and natural utterances for a given image. 
Moreover, these data sets typically record utterances that are more complex than a single word, such as image captions \cite{fangetal:2015,devlin:imcaqui,Bernardietal:automatic}, referring expressions \cite{Kazemzadeh2014,mao15,Yu2016}, visual dialogues \cite{das2017visual,vries2017guesswhat} or image paragraphs \cite{krause2017hierarchical}. While object names occur in all of these data sets, they are not necessarily marked up and linked to the corresponding image regions. The overview in Section \ref{sec:survey}\cs{why is there a dot behind the section number?} will discuss corpora where the grounding of names to regions for objects is given, as in the case of \vgenome \cite{krishna2016visualgenome}, or where it can be easily derived, as in the case of referring expressions.

Our new collection, ManyNames, presented in Section \ref{sec:data} focuses on object names in isolation and is, therefore, substantially more controlled than typical data sets that are currently in use in L\&V. This controlled collection procedure allowed us to elicit many annotations for the same object from different annotators, resulting in a data set that is amenable to studying variation and preferences in naming systematically and on a large scale.

\begin{table*}[htb]
  \centering
  \begin{tabular}{lrrrrr}
    \toprule
    &   RefCoco/+  &  Flickr30kE &           VG &      VGmn &        MN \\
    \midrule
    \# objects & 50.000 & 243.801 & 3.781.232 & 25.315 & 25.315 \\
    naming vocab size &  5.004 &  10.423 &   105.441 &  1.061 &  7.970 \\
    av. annotations/object &      2.8 &       2.3 &         1.7 &      7.2 &     35.3 \\
    \% objects with n types $>$ 1 &      0.7 &       0.3 &         0.02 &      0.05 &      0.9 \\
    av. types/object &      1.9 &       1.4 &         1 &      1.1 &      5.7 \\
    \bottomrule
  \end{tabular}
  \caption{Overview statistics for different data sets containing object naming data. VGmn shows statistics for the subset of \vg that overlaps with our ManyNames dataset.\label{tab:compare}}
\end{table*}

### 2019-11-29 papers/LREC2020/survey.tex

We identified three previously existing resources that can be of use for analysis and modeling of object naming: RefCOCO (and a variant, RefCOCO+), Flickr30k Entities, and Visual Genome.%
%\footnote{Other resources, such as \gbt{imagenet, openimages, see the other datasets cited in the openimages dataset}, provide object categories, rather than names.}
% footnote not necessary! this is explained in the background section
Table~\ref{tab:compare} summarizes their main characteristics and compares them to our dataset (last two columns; see Section~\ref{sec:data}).
As the table shows, previous datasets provide between one and three annotations per object, which, we believe, is not enough to assess naming behavior for individual instances.
This motivates our data collection. %, in which we collect 36 names per object.
However, because these datasets can be useful to examine other aspects of object naming, we summarize their characteristics below.

@@

Both datasets use the \referit\cite{Kazemzadeh2014} game for collecting referring expressions (RE) for natural objects in real-world images, and are built on top of the MS COCO \cite{mscoco}, 
%The latter provides five captions for each of  $300k$~images, spanning $80$~of the COCO categories.  
%However, the COCO region-level (object) annotations are not linked to the captions.
a dataset of images of natural scenes of $91$~common object categories (e.g.,~\cat{dog, pizza, chair}). 
The REs were collected via crowdsourcing in a two-player reference game designed to obtain REs uniquely referring to the target object. 
Specifically, a director and a matcher are presented with an image, and the director produces a RE for an outlined target object in the image. 
The matcher must click on the object he thinks the RE refers to. % (For more details on the datasets see \cite{Yu2016}). 
REs in \refcoco/+ were collected under the constraints that (i) all images contain at least two objects of the same category (80 COCO categories), which prompts the players to avoid the mere object category as RE, and (ii) in \refcocop the players must not use location words, urging them to refer to the appearance of objects.
 % \gbt{How come the naming vocabulary size is so large if RefCOCO contains only 80 categories? How did you compute these numbers, are they for names, or whole REs?} \sz{well, 80 categories doesn't mean much as the categories can be very general (like "human") ... and it nicely shows that natural names are much more variable than strict categories}
% Another critical property of the data is that, (iii), not all objects in an image were annotated with REs, may it due to the frequency constraint~(i), or due to the object not being part of the 80 COCO categories.

We expect this dataset to be good to examine the effect of distractors on naming choices in a referential setting, because images contain distractors.
Moreover, multiple annotations (2.84 on average) allow for some minimal analysis of naming variation.
However, note that not all objects are annotated with REs and corresponding categories, so it may be difficult to analyze the effect of distractors with automatic processing.
Names elicited in \refcoco should be natural, but it is unclear how the additional constraints in \refcocop impact on the naturalness of object naming.
Finally, the main drawback of this dataset is that the set of categories included is quite small ($80$~COCO categories).
To sum up, we would recommend \refcoco to study the effect of distractors on object naming in a restricted set of categories.

@@

This dataset has three main differences with respect to \refcoco/+: (1) the entity mentions were obtained via an image description task (captioning), as opposed to a referential task; (2) the images and the production of entity mentions were not subject to any constraints; (3) a much wider range of categories are covered (cf.\ the number of objects and the vocabulary size). %\gbt{Any idea what kind of categories are covered in \flickr?}
Moreover, although no exhaustive annotations of the images are available, the dataset does contain information for the most salient objects in the image, as they are typically mentioned in the captions.
The number of annotations per object, 2.3 annotations, is comparable to \refcoco.

@@

\vgenome \cite{krishna2016visualgenome} is one of the most densely and richly annotated resources currently available in L\&V; here, we focus on aspects immediately relevant to object naming.
%In the following, we will focus on describing aspects immediately relevant to object naming only, but many other annotations are available as well (e.g. questions, paragraphs, etc.)
%\paragraph{Collection and annotation procedure}
\vg aims at providing a full set of descriptions of the scenes which images depict in order to spur complete scene understanding. 
The data collection followed a complex procedure, involving many different rounds of annotation.
The first round of the procedure, and the basic backbone for the further rounds, is a collection of region-based descriptions: workers were asked to describe regions in the image and draw boxes around the corresponding area in the image (for examples, see Figure \ref{fig:bird}).

@@

\gbt{@Sina, pls check that I got this right:}
One of the main advantages of \vg are its size, with 3.8 million objects as opposed to 50K and 243K for the other two datasets, and its category coverage, with a vocabulary of object names of 105K compared to 5K/10K.
Another is the fact that it potentially provides exhaustive annotations of objects in the image, often with several region descriptions and possibly object names per object.
This should make it easier to identify factors intervening in naming choices.
However, there is a crucial pitfall: As Figure \ref{fig:bird} shows, there is only a partial linking of objects that are mentioned across different region descriptions; for instance, the first, second, and fifth object IDs in the figure actually correspond to the same object.
Moreover, the regions for the beak of the object (third and fourth object IDs) overlap with those of the bird.
This means that the identity of objects cannot be established based on the annotation, which severely limits the usefulness of the data to analyze contextual factors for naming.

\subsection{Discussion}

As the discussion above showed, while some existing resources can be used to shed light on factors affecting naming choices, they do not provide enough data to assess instance-specific naming behavior: To what extent do different people choose the same name for an object? How much variation is there, for specific instances? What factors affect this variation? How does that impact modeling in L\&V?
To answer these sorts of questions, we need naming data from many subjects for the same instances.
This is the motivation for our dataset, ManyNames, an augmentation of \vg.

>>>>

\cs{If space allows, I would also put an example image+annotation for RefCOCO and Flickr30kE}

We identified three previously existing resources that can be of use for analysis and modeling of object naming: RefCOCO (and a variant, RefCOCO+), Flickr30k Entities, and Visual Genome. %
%\footnote{Other resources, such as \gbt{imagenet, openimages, see the other datasets cited in the openimages dataset}, provide object categories, rather than names.}
% footnote not necessary! this is explained in the background section
Table~\ref{tab:compare} summarizes their main characteristics and compares them to our dataset (last two columns; see Section~\ref{sec:data}).
As the table shows, previous datasets provide between one and three annotations per object, which, we believe, is not enough to assess naming behavior for individual instances.
This motivates our data collection. %, in which we collect 36 names per object.
Since these datasets can, however, be useful to examine other aspects of object naming, we summarize their characteristics below.

@@

Both datasets use the \referit\cite{Kazemzadeh2014} game for collecting referring expressions (RE) for natural objects in real-world images, and are built on top of MS COCO \cite{mscoco}, 
%The latter provides five captions for each of  $300k$~images, spanning $80$~of the COCO categories.  
%However, the COCO region-level (object) annotations are not linked to the captions.
a dataset of images of natural scenes of $91$~common object categories (e.g.,~\cat{dog, pizza, chair}). 
The REs were collected via crowdsourcing in a two-player reference game designed to obtain REs uniquely referring to the target object. 
Specifically, a director and a matcher are presented with an image, and the director produces a RE for an outlined target object in the image. 
The matcher must click on the object he thinks the RE refers to. % (For more details on the datasets see \cite{Yu2016}). 
REs in \refcoco/+ were collected under the constraints that (i) all images contain at least two objects of the same category (80 COCO categories), which prompts the players to avoid the mere object category as RE, and (ii) in \refcocop the players must not use location words, urging them to refer to the appearance of objects.
 % \gbt{How come the naming vocabulary size is so large if RefCOCO contains only 80 categories? How did you compute these numbers, are they for names, or whole REs?} \sz{well, 80 categories doesn't mean much as the categories can be very general (like "human") ... and it nicely shows that natural names are much more variable than strict categories}
% Another critical property of the data is that, (iii), not all objects in an image were annotated with REs, may it due to the frequency constraint~(i), or due to the object not being part of the 80 COCO categories.

We expect this dataset to be good to examine the effect of distractors on naming choices in a referential setting, because images contain distractors. \cs{what does this mean, maybe give example?, e.g., from above with dog and dalmatian or so; otherwise the issue with the following part may not be understood}
Moreover, multiple annotations ($2.84$\ on average) allow for some minimal analysis of naming variation.
However, note that not all objects of an image are annotated with REs and corresponding categories, so it may be difficult to analyze the effect of distractors with automatic processing.
While in \refcoco, the elicited names can assumed to be natural, it is unclear how the additional constraints in \refcocop impact on the naturalness of object naming.
Finally, the main drawback of this dataset is that the set of categories included is quite small ($80$~COCO categories).
To sum up, we would recommend \refcoco to study the effect of distractors on object naming in a restricted set of categories.

@@

This dataset has three main differences with respect to \refcoco/+: (1) the entity mentions were obtained via an image description task (captioning), as opposed to a referential task; (2) the images and the production of entity mentions were not subject to any constraints; (3) a much wider range of categories are covered (cf.\ the number of objects and the vocabulary size in Table\ \ref{tab:compare}). %\gbt{Any idea what kind of categories are covered in \flickr?}
Moreover, although no exhaustive annotations of the images are available, the dataset does contain information for the most salient objects in the image, as they are typically mentioned in the captions.
The number of annotations per object, $2.3$\ annotations, is comparable to \refcoco.

@@

\vgenome (VG, \newcite{krishna2016visualgenome}) is one of the most densely and richly annotated resources currently available in L\&V; here, we focus on aspects immediately relevant to object naming.
%In the following, we will focus on describing aspects immediately relevant to object naming only, but many other annotations are available as well (e.g. questions, paragraphs, etc.)
%\paragraph{Collection and annotation procedure}
\vg aims at providing a full set of descriptions of the scenes which images depict in order to spur complete scene understanding. 
The data collection followed a complex procedure, involving many different rounds of annotation.
The first round of the procedure, and the basic backbone for the further rounds, is a collection of region-based descriptions: workers were asked to describe regions in the image and draw boxes around the corresponding area in the image (for examples, see Figure \ref{fig:bird}).

@@

\gbt{@Sina, pls check that I got this right:}
One of the main advantages of \vg are its size, with 3.8 million objects as opposed to 50K and 243K for the other two datasets, and its category coverage, with a vocabulary of object names of 105K compared to 5K/10K.
Another is the fact that it potentially provides exhaustive annotations of objects in the image, often with several region descriptions and possibly object names per object.
This should make it easier to identify factors intervening in naming choices.
However, there is a crucial pitfall: As Figure \ref{fig:bird} shows, there is only a partial linking of objects that are mentioned across different region descriptions; for instance, the first, second, and fifth object IDs in the figure actually correspond to the same object.
Moreover, the regions for the beak of the object (third and fourth object IDs) overlap with those of the bird.
This means that the identity of objects cannot be established based on the annotation, which severely limits the usefulness of the data to analyze contextual factors for naming.\cs{The explanation of intervening factors in object naming in the background may be a bit more detailed, such as to really understand the drawbacks of the existing datasets with respect to distractors.}

\subsection{Discussion}
\cs{@Sina I changed some stuff here, maybe you prefer the old version...}
As the discussion above showed, while some existing resources can be used to shed light on factors affecting naming choices, they do not provide enough data to assess instance-specific naming behavior: To what extent do different people choose the same name for an object \cs{instance?}? How much variation is there, for specific instances? 
To answer these sorts of questions, we need naming data from many subjects for the same instances. 
And, what factors affect observed naming variations (e.g.,\ the category or salience of other objects)? How does that impact the modeling of natural language in L\&V? 
Additional, dense annotations of images would be beneficial for these kinds of analyses.  
These are the motivations for our dataset, ManyNames, and for building it on top of \vg.
